% !TEX program = pdflatex
% =====================================================================
%  TwA Research Webinar — Emily's econ-audit segment (~18 min)
%  June 15, 2026.  Reframe of UVM Session 2 deck (Demo 2 centered).
%  Preamble matches Session2_Slides/session_2_slides.tex (shared design).
% =====================================================================
\documentclass[aspectratio=169, 10pt]{beamer}

%% ============================================================
%% PACKAGES
%% ============================================================
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{tikz}
\usetikzlibrary{positioning, calc, arrows.meta, shapes.geometric, fit, shadows}
\usepackage[most]{tcolorbox}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{pifont}

\graphicspath{{figures/}}

%% ============================================================
%% COLOR DEFINITIONS
%% ============================================================
\definecolor{UVMGreen}{HTML}{154734}
\definecolor{UVMGold}{HTML}{D4A84B}
\definecolor{SlateTeal}{HTML}{1B4D5C}
\definecolor{DeepCharcoal}{HTML}{2C3E50}
\definecolor{SoftCoral}{HTML}{C0534D}
\definecolor{CoolGray}{HTML}{8899A6}
\definecolor{PaleSage}{HTML}{EDF2F0}
\definecolor{LightGold}{HTML}{FDF6E3}
\definecolor{DarkSlate}{HTML}{0F2B36}
\definecolor{AccentBlue}{HTML}{3498DB}

%% ============================================================
%% BEAMER THEME SETUP
%% ============================================================
\setbeamercolor{structure}{fg=SlateTeal}
\setbeamercolor{normal text}{fg=DeepCharcoal}
\setbeamercolor{frametitle}{fg=SlateTeal}
\setbeamercolor{title}{fg=SlateTeal}
\setbeamercolor{subtitle}{fg=UVMGold}
\setbeamercolor{author}{fg=DeepCharcoal}
\setbeamercolor{date}{fg=CoolGray}
\setbeamercolor{institute}{fg=CoolGray}
\setbeamercolor{footline}{fg=CoolGray}
\setbeamercolor{block title}{fg=white, bg=SlateTeal}
\setbeamercolor{block body}{bg=PaleSage}
\setbeamercolor{alerted text}{fg=SoftCoral}
\setbeamercolor{item}{fg=SlateTeal}
\setbeamercolor{subitem}{fg=CoolGray}

\setbeamerfont{title}{size=\Large, series=\bfseries}
\setbeamerfont{subtitle}{size=\normalsize}
\setbeamerfont{frametitle}{size=\large, series=\bfseries}
\setbeamerfont{footline}{size=\tiny}

\setbeamertemplate{navigation symbols}{}

% Custom frame title
\setbeamertemplate{frametitle}{%
  \vskip14pt%
  \nointerlineskip%
  {\usebeamerfont{frametitle}\usebeamercolor[fg]{frametitle}\insertframetitle\par}%
  \vskip2pt%
  {\color{UVMGold}\rule{\textwidth}{1.2pt}}%
  \vskip3pt%
}

% Custom footline
\setbeamertemplate{footline}{%
  \begin{beamercolorbox}[wd=\paperwidth, ht=16pt, right, rightskip=1.5cm]{footline}%
    \usebeamerfont{footline}\insertframenumber\,/\,\inserttotalframenumber\vskip3pt%
  \end{beamercolorbox}%
}

% Itemize styles
\setbeamertemplate{itemize item}{\color{SlateTeal}\raisebox{0.15ex}{\small$\blacktriangleright$}}
\setbeamertemplate{itemize subitem}{\color{CoolGray}\raisebox{0.1ex}{\footnotesize$\bullet$}}

% Compact tcolorbox defaults
\tcbset{
  keybox/.style={
    colback=PaleSage, colframe=SlateTeal, boxrule=0.8pt, arc=3pt,
    left=6pt, right=6pt, top=4pt, bottom=4pt,
    fonttitle=\bfseries\small\color{white}, coltitle=white, colbacktitle=SlateTeal,
  },
  accentbox/.style={
    colback=LightGold, colframe=UVMGold, boxrule=0.8pt, arc=3pt,
    left=6pt, right=6pt, top=4pt, bottom=4pt,
  },
  quotebox/.style={
    colback=PaleSage, colframe=SlateTeal!50, boxrule=0.5pt, arc=2pt,
    left=8pt, right=8pt, top=4pt, bottom=4pt,
    borderline west={3pt}{0pt}{UVMGold},
  },
  coralbox/.style={
    colback=SoftCoral!8, colframe=SoftCoral, boxrule=0.8pt, arc=3pt,
    left=6pt, right=6pt, top=3pt, bottom=3pt,
    fonttitle=\bfseries\small\color{white}, coltitle=white, colbacktitle=SoftCoral,
  },
}

%% ============================================================
%% METADATA
%% ============================================================
\title{AI as an Adversarial Reader}
\subtitle{Auditing Code and Papers Before You Submit}
\author{Emily Beam}
\institute{Thinking with Agents \;$\cdot$\; Research Webinar}
\date{June 15, 2026}

\begin{document}

%% ====== SLIDE 1: TITLE ======
{
\setbeamertemplate{footline}{}
\begin{frame}[plain]
\begin{tikzpicture}[remember picture, overlay]
  \fill[SlateTeal] (current page.north west) rectangle (current page.south east);
  \fill[UVMGold] ([yshift=0.3cm]current page.center -| current page.west) rectangle ([yshift=0.25cm]current page.center -| current page.east);
  \node[anchor=center, text=white, font=\fontsize{26}{32}\bfseries\selectfont]
    at ([yshift=2.2cm]current page.center) {AI as an Adversarial Reader};
  \node[anchor=center, text=UVMGold, font=\fontsize{14}{19}\selectfont]
    at ([yshift=1.25cm]current page.center) {Auditing Code \& Papers Before You Submit};
  \node[anchor=center, text=white, font=\large\bfseries]
    at ([yshift=-0.6cm]current page.center) {Emily Beam};
  \node[anchor=center, text=PaleSage, font=\normalsize]
    at ([yshift=-1.3cm]current page.center) {University of Vermont \;$\cdot$\; Thinking with Agents};
  \node[anchor=center, text=CoolGray!70!white, font=\small]
    at ([yshift=-2.2cm]current page.center) {Research Webinar \quad$\cdot$\quad June 15, 2026};
  \node[text=white, opacity=0.04, font=\fontsize{100}{100}\selectfont, anchor=center, rotate=-15]
    at ([xshift=5cm, yshift=1.5cm]current page.center) {\faRobot};
\end{tikzpicture}
\end{frame}
}

%% ====== SLIDE 2: WHAT I'LL SHOW ======
\begin{frame}{What I'll Show You}
\begin{columns}[T]
\begin{column}{0.52\textwidth}
\vskip4pt
One real project --- a remote-education paper I've been trying to publish --- and two ways I used AI on it:
\vskip6pt
\begin{tcolorbox}[keybox, title={\faCode\quad 1. Audit the code}]
\small Turn 3 years of accumulated do-files into a clean, reproducible replication package --- and find bugs along the way.
\end{tcolorbox}
\vskip4pt
\begin{tcolorbox}[keybox, title={\faSearch\quad 2. Audit the paper}]
\small Adversarial referee-style review \emph{before} resubmitting --- then check it against the real referee reports.
\end{tcolorbox}
\end{column}
\begin{column}{0.42\textwidth}
\begin{tcolorbox}[accentbox]
\small
\textbf{The theme:}
\vskip4pt
AI as a fast, tireless \textbf{adversarial reader} of work you've already done.
\vskip4pt
You stay the expert. It does the mechanical reading and cross-checking --- at a scale and patience you can't match.
\end{tcolorbox}
\vskip4pt
{\scriptsize\color{CoolGray} Erkmen follows: AI at the \textit{front} end --- brainstorming and pressure-testing ideas before you've written anything.}
\end{column}
\end{columns}
\end{frame}

%% ====== SECTION DIVIDER: CODE AUDIT ======
{
\setbeamertemplate{footline}{}
\setbeamercolor{background canvas}{bg=SlateTeal}
\begin{frame}[plain, noframenumbering]
\centering\vfill
{\fontsize{22}{28}\bfseries\selectfont\color{white} Part 1}\\[6pt]
{\color{UVMGold}\rule{5cm}{0.8pt}}\\[6pt]
{\normalsize\color{UVMGold} Auditing a Replication Package}\\[4pt]
{\small\color{PaleSage} Bangladesh Remote Education RCT}
\vfill
\end{frame}
}

%% ====== SLIDE 3: CODE AUDIT — BEFORE ======
\begin{frame}[fragile]{Before: 3 Years of Accumulated Code}
\vskip-4pt
\begin{columns}[T]
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[colback=DarkSlate, colframe=SoftCoral, boxrule=0.8pt, arc=2pt,
  left=4pt, right=4pt, top=3pt, bottom=3pt]
{\color{CoolGray}\ttfamily\tiny
02\_Do files/\\
\quad 01\_master\_5th June 2021.do\\
\quad 03\_vargen\_07sep.do\\
\quad 03\_vargen.do\\
\quad 05\_endline balance\_eb.do\\
\quad 05\_endline balance.do\\
\quad 09\_attrition\_8 July\_e.do\\
\quad 09\_attrition\_8 July.do\\
\quad ...\\
\quad Archive/ {\color{CoolGray!50}(18 files)}\\
\quad WB Submission Files/ {\color{CoolGray!50}(14 copies)}
}
\end{tcolorbox}
\end{column}
\begin{column}{0.47\textwidth}
{\small\color{SoftCoral}\textbf{The problems:}}
\vskip3pt
\small
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{51 do-files} across 4 subdirectories
  \item Master file from \textbf{June 2021} --- 3 years stale
  \item Date-in-filename: \texttt{\_07sep}, \texttt{\_02July1130am}
  \item Author-in-filename: \texttt{\_eb}, \texttt{\_e}
  \item Hardcoded paths --- only runs on my machine
  \item No documentation, no version control
\end{itemize}
\vskip3pt
\begin{tcolorbox}[quotebox, top=2pt, bottom=2pt]
\scriptsize This is \textbf{extremely common} in economics. You probably have a project that looks like this.
\end{tcolorbox}
\end{column}
\end{columns}
\end{frame}

%% ====== SLIDE 4: CODE AUDIT — AFTER ======
\begin{frame}[fragile]{After: One Clean, Reproducible Pipeline}
\vskip-4pt
\begin{columns}[T]
\begin{column}{0.47\textwidth}
{\scriptsize
\begin{tabular}{>{\raggedright\arraybackslash}m{2.8cm} >{\centering\arraybackslash}m{1.5cm} >{\centering\arraybackslash}m{1.5cm}}
\rowcolor{SlateTeal}
\textcolor{white}{\textbf{Dimension}} & \textcolor{white}{\textbf{Before}} & \textcolor{white}{\textbf{After}} \\[1pt]
\rowcolor{PaleSage}
Do-files & 51 & \textbf{8} \\[1pt]
\rowcolor{white}
Master file & 2021 & Current \\[1pt]
\rowcolor{PaleSage}
Config system & None & Template \\[1pt]
\rowcolor{white}
Version control & None & Git \\[1pt]
\rowcolor{PaleSage}
Documentation & None & Full \\[1pt]
\rowcolor{white}
``Which version?'' & Constant & \textbf{Zero} \\[1pt]
\end{tabular}
}
\vskip3pt
\begin{tcolorbox}[accentbox, top=2pt, bottom=2pt]
\scriptsize \textbf{86 old variants} preserved in Archive/ --- nothing deleted, fully reversible.
\end{tcolorbox}
\end{column}
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[colback=DarkSlate, colframe=DarkSlate, arc=2pt,
  left=4pt, right=4pt, top=2pt, bottom=2pt]
{\color{CoolGray}\ttfamily\tiny
bd-remote-ed/\\
\; code/00\_master\_repo.do\\
\; code/07\_Dofiles\_academic/\\
\;\quad \_globals.do, 02\_datagen.do,\\
\;\quad 03\_vargen.do {\color{UVMGold!70}(THE one)}, ...\\
\;\quad Archive/ {\color{CoolGray!50}(86 old)}\\
\; config/config\_local\_template.do\\
\; docs/ \;\; justfile \;\; README.md
}
\end{tcolorbox}
\vskip3pt
\begin{tcolorbox}[quotebox, top=2pt, bottom=2pt]
\scriptsize \textbf{Time:} $\sim$2 Claude Code sessions (a few hours).
\textbf{By hand:} days, minimum.
\end{tcolorbox}
\end{column}
\end{columns}
\end{frame}

%% ====== SLIDE 5: THE $FLAGS BUG ======
\begin{frame}[fragile]{The Bug It Found: A Typo Hiding in Plain Sight}
\vskip-2pt
\begin{tcolorbox}[keybox, title={\faBug\quad The \texttt{\$flags} variable list}, top=2pt, bottom=2pt]
\small
\texttt{\$flags} = 17 missing-value indicators used as controls in \textbf{every regression}. Defined independently in 5 scripts.
\end{tcolorbox}
\vskip3pt
\begin{columns}[T]
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[colback=SoftCoral!8, colframe=SoftCoral, boxrule=0.5pt, arc=2pt, left=5pt, right=5pt, top=3pt, bottom=3pt]
\centering{\small\color{SoftCoral}\textbf{3 of 5 scripts (wrong):}}
\vskip3pt
{\ttfamily\small\color{DeepCharcoal}
... \_f\_c\_engaged \_f\_c\_health\\
\colorbox{SoftCoral!20}{\_c\_child\_work}}
\vskip2pt
{\scriptsize Missing the \texttt{\_f\_} prefix}
\end{tcolorbox}
\end{column}
\begin{column}{0.06\textwidth}
\centering\vskip0.8cm
{\large\color{UVMGold}\faArrowRight}
\end{column}
\begin{column}{0.42\textwidth}
\begin{tcolorbox}[colback=PaleSage, colframe=SlateTeal!50, boxrule=0.5pt, arc=2pt, left=5pt, right=5pt, top=3pt, bottom=3pt]
\centering{\small\color{SlateTeal}\textbf{Correct:}}
\vskip3pt
{\ttfamily\small\color{DeepCharcoal}
... \_f\_c\_engaged \_f\_c\_health\\
\colorbox{PaleSage!50}{\_f\_c\_child\_work}}
\end{tcolorbox}
\end{column}
\end{columns}
\vskip3pt
\begin{tcolorbox}[quotebox, top=2pt, bottom=2pt]
\scriptsize \textbf{Result:} \texttt{\_c\_child\_work} appeared \textit{twice} in regressions; the real missing indicator was left out. Survived 10+ versions across 2+ years. No error, no crash --- just quietly wrong.
\textbf{How AI found it:} cross-referencing every \texttt{global flags} definition across all 51 files.
\end{tcolorbox}
\end{frame}

%% ====== SECTION DIVIDER: PAPER AUDIT ======
{
\setbeamertemplate{footline}{}
\setbeamercolor{background canvas}{bg=SlateTeal}
\begin{frame}[plain, noframenumbering]
\centering\vfill
{\fontsize{22}{28}\bfseries\selectfont\color{white} Part 2}\\[6pt]
{\color{UVMGold}\rule{5cm}{0.8pt}}\\[6pt]
{\normalsize\color{UVMGold} Auditing the Paper}\\[4pt]
{\small\color{PaleSage} Can AI Referee Your Own Work?}
\vfill
\end{frame}
}

%% ====== SLIDE 6: WHAT IS /ECON-AUDIT ======
\begin{frame}[fragile]{What Is \texttt{/econ-audit}?}
\vskip-2pt
\begin{columns}[T]
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[keybox, title={\faSearch\quad An Adversarial Review Skill}, top=3pt, bottom=3pt]
\small
A reusable skill that reads a paper and acts as a \textbf{skeptical referee}.
\vskip3pt
\begin{itemize}\setlength{\itemsep}{1pt}
  \item Reads the full paper (LaTeX, tables, appendix)
  \item Checks identification, power, measurement
  \item Produces a structured audit report
  \item Takes $\sim$60 seconds
\end{itemize}
\end{tcolorbox}
\vskip3pt
\begin{tcolorbox}[colback=DarkSlate, colframe=DarkSlate, arc=2pt,
  left=4pt, right=4pt, top=2pt, bottom=2pt]
{\color{CoolGray}\ttfamily\scriptsize \$ npx skills add eabeam/econ-skills \textbackslash\\
\quad\quad --skill econ-audit}
\end{tcolorbox}
\end{column}
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[accentbox, top=3pt, bottom=3pt]
\small
\textbf{What it checks:}
\vskip3pt
\begin{enumerate}\setlength{\itemsep}{1pt}
  \item \textbf{Identification:} Is the causal claim valid?
  \item \textbf{Statistics:} MHT, power, attrition
  \item \textbf{Measurement:} Are variables measured well?
  \item \textbf{Methodology:} Design consistency
  \item \textbf{Presentation:} Framing, length
\end{enumerate}
\end{tcolorbox}
\end{column}
\end{columns}
\end{frame}

%% ====== SLIDE 7: THE AUDIT OUTPUT (shown from saved run) ======
\begin{frame}[fragile]{Running It on the Paper: 5 Critical, 8 Important, 6 Minor}
\vskip-2pt
\begin{columns}[T]
\begin{column}{0.40\textwidth}
\begin{tcolorbox}[colback=DarkSlate, colframe=CoolGray!40, boxrule=0.5pt, arc=3pt,
  left=6pt, right=6pt, top=5pt, bottom=5pt]
{\color{CoolGray}\ttfamily\small\$\; claude}\\[3pt]
{\color{white}\ttfamily\small /econ-audit main.tex}
\end{tcolorbox}
\vskip4pt
{\scriptsize\color{CoolGray} Output shown is from a saved run --- AI output varies between runs, so I pin the version I'm reasoning about.}
\end{column}
\begin{column}{0.55\textwidth}
\small Three of the critical findings:
\vskip3pt
\begin{tcolorbox}[coralbox, title={\faExclamationTriangle\quad Critical}, top=3pt, bottom=3pt]
\footnotesize
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{A1 --- Identification:} the mediation claim (info $\rightarrow$ tutoring $\rightarrow$ learning) is not identified.
  \item \textbf{B1--B3 --- Statistics:} no MHT adjustment across domains; headline effect below the MDE; underpowered heterogeneity drives the inequality story.
  \item \textbf{C1 --- Measurement:} differential attrition in the learning sample ($p<0.001$); suggested Lee bounds.
\end{itemize}
\end{tcolorbox}
\end{column}
\end{columns}
\end{frame}

%% ====== SLIDE 8: AI AUDIT VS REAL REFEREES ======
\begin{frame}{AI Audit vs.\ Real Referees: 7 of 10 in $\sim$60 Seconds}
\vskip-2pt
{\scriptsize
\begin{tabular}{>{\raggedright\arraybackslash}m{5.5cm} c >{\raggedright\arraybackslash}m{5.2cm}}
\rowcolor{SlateTeal}
\textcolor{white}{\textbf{Referee Criticism}} & \textcolor{white}{\textbf{AI?}} & \textcolor{white}{\textbf{Notes}} \\[2pt]
\rowcolor{PaleSage}
High attrition \& differential attrition & \textcolor{SlateTeal}{\faCheck} & Flagged as Critical; suggested Lee bounds \\[2pt]
\rowcolor{white}
Results don't tell a coherent story & \textcolor{UVMGold}{\faAdjust} & Caught ID problem, missed internal contradictions \\[2pt]
\rowcolor{PaleSage}
Theoretical model not useful & \textcolor{SlateTeal}{\faCheck} & Flagged --- but recommended \textit{including} it \\[2pt]
\rowcolor{white}
Short intervention duration (4--8 weeks) & \textcolor{SoftCoral}{\faTimes} & Requires field knowledge \\[2pt]
\rowcolor{PaleSage}
Noisy learning measures (8-item phone test) & \textcolor{SlateTeal}{\faCheck} & Strong match; flagged IRT minimums \\[2pt]
\rowcolor{white}
Paper too long and hard to follow & \textcolor{SlateTeal}{\faCheck} & Suggested cutting 20--30\% \\[2pt]
\rowcolor{PaleSage}
Multiple hypothesis testing issues & \textcolor{SlateTeal}{\faCheck} & Aggressive; added winner's curse framing \\[2pt]
\rowcolor{white}
Limited external validity / COVID fatigue & \textcolor{UVMGold}{\faAdjust} & Partial; missed publication landscape \\[2pt]
\rowcolor{PaleSage}
Deviations from pre-analysis plan & \textcolor{SlateTeal}{\faCheck} & Caught the spirit, not the specifics \\[2pt]
\rowcolor{white}
Complex randomization hard to interpret & \textcolor{SlateTeal}{\faCheck} & Strong match \\[2pt]
\end{tabular}
}
\vskip3pt
\begin{tcolorbox}[accentbox, top=2pt, bottom=2pt, width=12cm]
\centering\small \textbf{5 full matches, 2 partial, 1 opposite recommendation, 2 misses.}\\
11 referee reports across 8 journals over 4 years --- vs.\ 60 seconds of AI.
\end{tcolorbox}
\end{frame}

%% ====== SLIDE 9: WHAT THE AI MISSED ======
\begin{frame}{What the AI Missed --- And Why It Matters}
\begin{columns}[T]
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[coralbox, title={\faTimes\quad The Misses}, top=4pt, bottom=4pt]
\small
\begin{itemize}\setlength{\itemsep}{4pt}
  \item \textbf{Short duration:} 4--8 weeks is unusually short for an education RCT. Requires knowing field norms.
  \item \textbf{Internal contradictions:} the data arm raised tutoring \textit{more} than the info arm, yet only info improved learning. Referees caught this; AI didn't.
  \item \textbf{COVID fatigue:} ``we've seen too many of these.'' AI can't read the publication landscape.
\end{itemize}
\end{tcolorbox}
\end{column}
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[quotebox]
\small
\textbf{The opposite advice:}\\[3pt]
The AI recommended \textit{including} the conceptual model. Every referee wanted it \textbf{cut}.
\vskip4pt
Sometimes AI gives exactly the wrong recommendation --- because it lacks field conventions.
\end{tcolorbox}
\vskip4pt
\begin{tcolorbox}[accentbox]
\small
\textbf{Pattern:}\\[2pt]
AI reliably catches \textbf{statistical / econometric} issues.\\[2pt]
AI misses \textbf{field knowledge}, \textbf{within-paper logic checks}, and \textbf{publication strategy}.
\end{tcolorbox}
\end{column}
\end{columns}
\end{frame}

%% ====== SLIDE 10: HONEST TAKEAWAY ======
\begin{frame}{Takeaway: A Very Good Pre-Submission Check}
\begin{columns}[T]
\begin{column}{0.50\textwidth}
\begin{tcolorbox}[keybox, title={\faCheck\quad What It Replaces}]
\small
\begin{itemize}\setlength{\itemsep}{3pt}
  \item The first 80\% of what a careful internal seminar discussant would say
  \item Catches the systematic stuff: identification, power, MHT, attrition
  \item In one minute, not one month
\end{itemize}
\end{tcolorbox}
\end{column}
\begin{column}{0.44\textwidth}
\begin{tcolorbox}[colback=SoftCoral!8, colframe=SoftCoral, boxrule=0.5pt, arc=3pt,
  left=6pt, right=6pt, top=4pt, bottom=4pt]
\small
\textbf{What it doesn't replace:}
\vskip3pt
\begin{itemize}\setlength{\itemsep}{2pt}
  \item Field-specific intuition
  \item ``Does this make sense given what we know about Bangladesh?''
  \item Publication strategy
  \item Colleagues who know your work
\end{itemize}
\end{tcolorbox}
\end{column}
\end{columns}
\vskip8pt
\begin{tcolorbox}[quotebox, width=13cm]
\small \textbf{Code audit:} it found bugs I hadn't found in two years. That alone justified the time.\\[2pt]
\textbf{Paper audit:} run it before you send a paper out. It's free, and it catches the embarrassing stuff.
\end{tcolorbox}
\end{frame}

%% ====== SLIDE 11: HANDOFF + RESOURCES ======
\begin{frame}[fragile]{Try It --- And Over to Erkmen}
\begin{columns}[T]
\begin{column}{0.50\textwidth}
\begin{tcolorbox}[keybox, title={\faRocket\quad What to Try First}]
\small
\begin{enumerate}\setlength{\itemsep}{3pt}
  \item Install \texttt{/econ-audit}, run it on your next submission --- before the referees do.
  \item Point Claude Code at a messy project folder and ask it to audit the structure.
\end{enumerate}
\end{tcolorbox}
\vskip4pt
\begin{tcolorbox}[quotebox, top=3pt, bottom=3pt]
\scriptsize Same principle both times: \textbf{AI does the mechanical reading; you keep the judgment.}
\end{tcolorbox}
\end{column}
\begin{column}{0.47\textwidth}
\begin{tcolorbox}[keybox, title={\faLink\quad Resources}, top=3pt, bottom=3pt]
\small
\begin{itemize}\setlength{\itemsep}{3pt}
  \item Econ skills:\\{\scriptsize\ttfamily github.com/eabeam/econ-skills}
  \item Skills library:\\{\scriptsize\ttfamily skills.sh}
  \item Claude Code docs:\\{\scriptsize\ttfamily docs.anthropic.com/en/docs/claude-code}
\end{itemize}
\end{tcolorbox}
\vskip4pt
{\small\color{SlateTeal} Next: Erkmen on using AI to \textbf{brainstorm and pressure-test research ideas}.}
\end{column}
\end{columns}
\end{frame}

\end{document}
